Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2024-09-10 Manuscript/src/sections/titleAbstract.tex
paper: Stefano's comments

    \title{Which PMV model should you use? Comparison of the ISO 7730:2005 and ASHRAE 55:2023 PMV models}
    % alternatives PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?
    % alternatives ISO 7730:2005 vs ASHRAE 55:2023: A comparison of the accuracy of the two implementations of the PMV model

    \author[label1,label2]{Federico Tartarini\corref{mycorrespondingauthor}}
    \ead{federico.tartarini@sydney.edu.au}
    \author[label3]{Stefano Schiavon}

    \address[label1]{University of Sydney, Sydney, AU}
    \address[label2]{Berkeley Education Alliance for Research in Singapore, Singapore}
    \address[label3]{Center for the Built Environment, University of California, Berkeley, CA, USA}

@@

    \begin{abstract}
%        The \ac{pmv} model was developed by Fanger more than 50 years ago to predict the mean thermal sensation of a group of people.
%        It is based on a heat balance model of the human body.

%        Being relatively simple to calculate and included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730}.
        It has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one is the \ac{pmv-ce}.
        The \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion.
%        for many users who often struggle to determine which model is most appropriate for their needs.
        Which model is more accurate?
        Which model should you use?

        We compared the accuracy of the two \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        Based on our results, we recommend using the original \ac{pmv} instead of the \ac{pmv-ce}, since the \ac{pmv-ce} provides no significant improvement over the original \ac{pmv} in predicting thermal sensation, despite its increased complexity.
%        Surprisingly, the bias of the \ac{pmv-ce} model was greater (a higher number is negative) than the \ac{pmv} when we only analyzed the entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\sec}.
        We suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$ since the \ac{pmv} model cannot determine the degree to which people are dissatisfied.
%        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale instead of the thermal sensation scale.
    \end{abstract}

>>>>

    \title{Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023}

    \author[label1]{Federico Tartarini\corref{mycorrespondingauthor}}
    \ead{federico.tartarini@sydney.edu.au}
    \author[label3]{Stefano Schiavon}

    \address[label1]{The University of Sydney, Sydney, AU}
    \address[label3]{Center for the Built Environment, University of California, Berkeley, CA, USA}

@@

    \begin{abstract}
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730}.
        It has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations. 
        One is the \ac{pmv-ce}.
        The \gls{7730} and \gls{55} are the most widely referenced thermal comfort standards worldwide, and their different \ac{pmv} formulations are a source of confusion.
        Which model is more accurate?

        We compared the accuracy of the two \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        Based on our results, we recommend using the original \ac{pmv} instead of the \ac{pmv-ce}, since the \ac{pmv-ce} provides no significant improvement over the original \ac{pmv} in predicting thermal sensation, even in the subset of data with \ac{v}~$\geq$~\qty{0.2}{\m\per\sec}.
        We suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$ since the \ac{pmv} model cannot determine the degree to which people are dissatisfied.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, the assumption that individuals who feel `slightly warm' or `slightly cool' can be considered thermally comfortable leads to under-counting thermal discomfort, therefore, we recommend using the thermal preference scale instead of the thermal sensation scale.
    \end{abstract}
